---
title: Dr.
name: André Calero Valdez
position: "Junior Research Group Leader, AkadOR"
address: "Maria-Theresia-Alle 19 -- 52064 Aachen, Germany"
mobile: +49 173-5963359
www: calerovaldez.com
email: andrecalerovaldez@gmail.com
profilepic: "../data/photo.jpeg"
twitter: sumidu
github: sumidu
aboutme: Data Science, Human-Computer Interaction, Information Visualization, Recommender Systems, Industry 4.0, Machine Learning, Social Networks, Technology Acceptance
date: "`r format(Sys.time(), '%B %Y')`"
classoption: "sans"
output: 
  pdf_document:
    keep_tex: true
    template: template/template.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(lubridate)
library(here)
library(readxl)
library(glue)
add.suffix <- function (x) if(day(x) %in% c(1, 21, 31)) { paste0(day(x), "st", format(x, "%B %Y"))
  } else if (day(x) %in% c(2, 22)){ paste0(day(x), "nd ", format(x, "%B %Y"))
  } else paste0(day(x), "th ", format(x, "%B %Y"))




```

```{r experience, inclue=FALSE}
# Data Loading ----
# Jobs ----
jobs.raw <- read_csv(here::here("data", "jobs.csv"))
jobs <-
  jobs.raw %>% 
  fill(Start, End, What, With, Where, Tag) %>%  
  mutate(Start = mdy(Start),
         End = mdy(End)) %>% 
  mutate(When = case_when(
    is.na(End) ~ glue("{year(Start)}--Present") %>% as.character(),
    year(Start) == year(End) ~ year(End) %>% as.character(),
    TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
  ))

# Teaching ----
teaching.raw <- read_csv(here::here("data", "teaching.csv"))
teaching <-
  teaching.raw %>% 
  fill(Start, End, What, With, Where, Tag) %>%  
  mutate(Start = mdy(Start),
         End = mdy(End)) %>% 
  mutate(When = case_when(
    is.na(End) ~ glue("{year(Start)}--Present") %>% as.character(),
    year(Start) == year(End) ~ year(End) %>% as.character(),
    TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
  ))

# Service ----
service.raw <- read_csv(here::here("data", "service.csv"))
service <-
  service.raw %>% 
  fill(Start, End, What, With, Where, Tag) %>%  
  mutate(Start = mdy(Start),
         End = mdy(End)) %>% 
  mutate(When = case_when(
    is.na(End) ~ glue("{year(Start)}--Present") %>% as.character(),
    year(Start) == year(End) ~ year(End) %>% as.character(),
    TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
  ))


# Reviews ----
reviews.raw <- read_csv(here::here("data", "reviews.csv"))

reviews <- reviews.raw %>% 
  fill(Type, Name)


# Memberships ---
memberships.raw <- read_csv(here::here("data", "memberships.csv"))
memberships <- memberships.raw %>% fill(Membership, Type)


# Google Publication Data ----
my_name <- "**André Calero Valdez**" # how the authors name is shown
name_aliases <- c("André Calero Valdez" = my_name,
                  "AC Valdez" = my_name, 
                  "A Calero Valdez" = my_name,
                  "A Calero-Valdez" = my_name
                  )
pub_cache <- here::here("data", "pubcache.RDS")
scholar_cache <- here::here("data", "scholarcache.RDS")
if(!file.exists(pub_cache)){
  publications <- scholar::get_publications("K6EVDoYAAAAJ")
  scholar_profile <- scholar::get_profile("K6EVDoYAAAAJ")
  write_rds(publications, pub_cache)
  write_rds(scholar_profile, scholar_cache)

} else {
  publications <- read_rds(pub_cache)
  scholar_profile <- read_rds(scholar_cache)
}


author_vars <- paste0("author_",1:20)

reverse_words <- function(string)
{
  # split string by blank spaces
  string_split = strsplit(as.character(string), split = ",")
  # how many split terms?
  string_length = length(string_split[[1]])
  # decide what to do
  if (string_length == 1) {
    # one word (do nothing)
    reversed_string = string_split[[1]]
  } else {
    # more than one word (collapse them)
    reversed_split = string_split[[1]][string_length:1]
    reversed_string = paste(reversed_split, collapse = " ")
  }
  # output
  return(reversed_string)
} 

# Formatting helper function (A, B; C, D -> B A, D C)
comma_switch <- function(x){
  if(is.na(x)) {
    return(NA)
  }
#  x <- c("Brauner, Philipp", "Calero, André")
  lapply(x, reverse_words)
}

unpublished.raw <- read_csv(here::here("data", "unpublished.csv"))

unpublished <- unpublished.raw %>% tidyr::separate(author, sep = ";|&", into=author_vars) %>% 
  rowwise() %>% 
  mutate_at(vars(author_vars),.funs = comma_switch) %>% 
  unite(col = "author", author_vars, sep = ", ", remove = T) %>% 
  mutate(author = str_replace_all(author, ", NA", "")) %>% 
  mutate(number = case_when(is.na(number) ~ "", 
                            !is.na(number) ~number)) %>% 
  mutate(cites = 0, pubid="") %>% 
  mutate(author = str_squish(author)) %>%  
  mutate(author = str_replace_all(author, name_aliases)) 


# Fix Publication Data
publications <- publications %>% 
  filter(!is.na(year)) %>% 
  mutate(author = str_replace_all(author, name_aliases)) 

# Remove ellipses
publications <- publications %>% 
  filter(!is.na(year)) %>% 
  mutate(author = str_replace_all(
    author, 
    c("…"="et al.", " \\.\\.\\."=" et al."))) 

# Change some typical mistakes
journal_corrections <- c("Managing.the.enterprise.of.the.…" = "Managing the enterprise of the Future",
                         "Human.Interface.and.the.Management.of.…" = "Human Interface and the Management of Information",
                         "International.Conference.on.Information.and.Communication.Technologies.…" =
                           "International Conference on Information and Communication Technologies for Ageing Well and eHealth",
                         "Business,.Government.*and.Organizations.…" = "Business, Government, and Organizations",
                         "Beiträge.der.…" = "Beiträge der Forschungspartner",
                         "economic.endeavor.…" = "economic endeavor",
                         "Human.Modeling.and.Applications.in.…" = 
                           "Human Modeling and Applications in Health, Safety, Ergonomics and Risk Management",
                         "Organisationen.in.Zeiten.des.…"= "Organisationen in Zeiten des demographischen Wandels")

publications <- publications %>% 
  mutate(journal = str_replace_all(
    journal, journal_corrections))
  
publications <- publications %>% 
  mutate(number = str_replace_all(
    number, c("…"="")))


publications <- publications %>% 
  mutate(title = str_replace_all(
    title, c("Credibility.of.Digital.Health.Information.and.the.…"="Credibility of Digital Health Information and the Influence of User Diversity")))

#publications <- publications %>% 
#  mutate(journal = case_when(str_length(journal)<1 ~ number,
#                             str_length(journal)> ~ journal))

publications <- publications %>% bind_rows(unpublished)

# Orcid Data ----
orcid_cache <- here::here("data", "orcidcache.RDS")
if(!file.exists(orcid_cache)){
  edu <- rorcid::orcid_educations("0000-0002-6214-1461")
  write_rds(edu, orcid_cache)
} else {
  edu <- read_rds(orcid_cache)
}


```

```{r presentations, include=FALSE}
presentations.raw <- read_csv(here("data", "presentations.csv"))
presentations <- 
  presentations.raw %>% 
  mutate(When = mdy(When))
```


# Personal Information

```{r, results="asis"}
pd_df <- tribble(~meta, ~input,
              "Date of Birth","22nd January 1981",
              "Marital Status", "Married",
              "Children", "1 Daughter (1 year old)",
              "Address", "Maria-Theresia-Allee 19",
              "", "52064 Aachen, Germany",
              "Email", "andrecalerovaldez@gmail.com",
              "www", "www.calerovaldez.com"
              )

brief_entries(pd_df, when = meta, what = input, with = " ")
```

\vspace{1em}

## Scholarly Metrics

```{r, results="asis"}
metrics_df <- tribble(~meta, ~input,
              "Citations", scholar_profile$total_cites,
              "h-index", scholar_profile$h_index,
              "i10-index", scholar_profile$i10_index,
              "Acquired 3rd party Funding", "approx. \\euro  1.3 Mio"
              )

brief_entries(metrics_df, when = meta, what = input, .protect = F)
```


<!-- # Education -->

```{r education2, eval=FALSE, include=FALSE}

edu$`0000-0002-6214-1461`$`education-summary` %>% 
  mutate(`end-date.year.value` = replace_na(`end-date.year.value`, "2019")) %>% 
  detailed_entries(
    what = `role-title`,
    when = glue::glue("{`start-date.year.value`} - {`end-date.year.value`}"), 
    with = organization.name,
    where = organization.address.city
  )
```

# Work Experience

```{r research}
jobs %>% 
  filter(Tag == "research") %>% 
  arrange(desc(Start)) %>% 
  detailed_entries(
    what = What,
    when = When,
    with = With,
    where = Where,
    why = Why
  )
```

# Scientific Degrees

```{r degrees}
jobs %>% 
  filter(Tag == "degree") %>% 
  arrange(desc(Start)) %>% 
  detailed_entries(
    what = What,
    when = When,
    with = With,
    where = Where,
    why = Why
  )
```


# Education

```{r education}
jobs %>% 
  filter(Tag == "education") %>% 
  arrange(desc(Start)) %>% 
  detailed_entries(
    what = What,
    when = When,
    with = With,
    where = Where,
    why = Why
  )
```


# Teaching Experience

```{r}
teaching %>%
  filter(Tag == "teaching", year(Start) > 2005) %>%
  arrange(desc(Start)) %>% 
  detailed_entries(
    what = What,
    when = When,
    with = With,
    where = Where,
    why = Why
  )
```

\vspace{1em}

## Invited Guest Lectures

```{r}
presentations %>% 
  filter(Tag == "lecture") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = When,
                   with = Conference,
                   where = Location,
                   why = Award)
```

# Grants, Awards and Honors

```{r}
read_csv(here("data", "awards and grants.csv")) %>% 
  mutate(year = str_extract(date, "\\d{4}")) %>% 
  arrange(desc(year)) %>% 
  brief_entries(what = award, when = date, with = with)
```

<!--- # Publications --->

```{r publications, eval=FALSE, include=FALSE}
publications %>%
  arrange(desc(year)) %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = paste0("",journal,""),
    .protect = T
  )

#bibliography_entries(here("data", "My Publications.bib"), title = NULL)
```

<!--- ## Software -->

```{r eval=FALSE, include=FALSE}
df <- tribble(~what, ~when, ~with, ~where, ~why,
              "Contributor to the `webchem` package by Eduard Szöcs et al.",
              2017,
              NA,
              "https://cran.r-project.org/web/packages/webchem/",
              "Contributed functions to scrape flavor percept data from flavor.net and to scrape retention indices from NIST given chemical identifier numbers",
              "Author of `chemhelper` package",
              2018,
              NA,
              "https://github.com/Aariq/chemhelper",
              "Provides wrapper functions for working with IonAnalytics deconvolution software as well as other R packages for multivariate analysis"
              )

df %>% 
  arrange(desc(when)) %>% 
  detailed_entries(what = what, when = when, with = with, where = where, why = why)
```

# Presentations

## Talks

```{r}
presentations %>% 
  filter(Tag == "talk") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}"),
                   with = Conference,
                   where = Location,
                   why = Award)
```

<!--- ## Posters -->

```{r}
presentations %>% 
  filter(Tag == "poster") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = When,
                   with = Conference,
                   where = Location,
                   why = Award)
```

<!---## Other -->

```{r}
presentations %>% 
  filter(Tag == "workshop") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = When,
                   with = Conference,
                   where = Location,
                   why = Award)
```



# Service

## Memberships

```{r}
memberships %>% 
  brief_entries(what=Membership, when=Type)
```


## Manuscript Reviews

```{r}
reviews %>% 
  filter(Type == "adhoc") %>% 
  pull(Name) %>% 
  collapse(sep = ", ") -> adhocs

reviews %>% 
  filter(Type == "editorial") %>% 
  pull(Name) %>% 
  collapse(sep = ", ") -> editorial

reviews %>% 
  filter(Type == "committee") %>% 
  pull(Name) %>% 
  collapse(sep = ", ") -> committee

review_df <- data.frame(Name=adhocs, Type="Adhoc reviews") %>%
  bind_rows(data.frame(Name=editorial, Type="Editorial-Board or Program Committee")) %>% 
  bind_rows(data.frame(Name=committee, Type="Head of Program Committee"))




review_df %>% 
  brief_entries(what=Name, when=Type)
```

## Academic Services

```{r}
service %>%
  filter(Tag == "service") %>% 
  detailed_entries(
    what = What,
    when = When,
    with = With,
    where = Where,
    why = Why
  )
```

# Bibliography
**Articles published by outlets with scientific quality assurance, book publications, and works accepted for publication but not yet published.**

Citations are retrieved from Google Scholar on `r add.suffix(Sys.Date())`. 

```{r, results="asis"}

formatEntry <- function(id, author, title, journal, number, cites, year, cid, pubid){
  res <- paste0(" 1. ")
  if(str_length(author)>0) {
    res <- paste0(res, author, " ")
  }
  if(str_length(year)>0) {
    res <- paste0(res, "(", year, "). ")
  }
  if(str_length(title)>0) {
    res <- paste0(res, title, ". ")
  }
  if(str_length(journal)>0) {
    res <- paste0(res, " In: *", journal, "*")
  }
  if(str_length(number)>0) {
    res <- paste0(res, ", ", number)
  }
  if(cites>0) {
      res <- paste0(res, " (cited ", cites, " times)")
  } 
  if(!is.na(cid)){
    if(cid=="(accepted)"){
      res <- paste0(res, " **(accepted)**")
    }
    if(cid=="(under revision)"){
      res <- paste0(res, " **(under revision)**")
    }
    if(cid=="(submitted)"){
      res <- paste0(res, " **(submitted)**")
    }
  }


  paste0(res, "\n")
}

publications <- publications %>% 
  arrange(desc(year)) %>% 
  mutate(id = 1:n()) %>% 
  rowwise() %>% 
  mutate(mdtext = formatEntry(id, author, title, journal, number, cites, year, cid, pubid)) 

publications %>%
  arrange(desc(year)) %>% 
  pull("mdtext") %>% cat()
```

